Fractional anisotropy as tracer of cosmic voids

### 2014-07-06 cosmic_voids.tex
New title and references
Changing scale of volume function of voids, effective radius instead of log10 volume

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Analysis of bulk void regions}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Fractional anisotropy as tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

%.........................................................................
%FIGURE 6: shape-distributions
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 6mm 8mm 5.5mm 4mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb_FAG.pdf}
  \includegraphics[trim = 6mm 8mm 5.5mm 4mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Vweb_FAG.pdf}

  \

  \includegraphics[trim = 6mm 8mm 5.5mm 4mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb_DLG.pdf}
